Analysis

### 2022-05-26 EDA_CTCFBSDB.Rmd
Change assemblies to hg18 and mm8

# Input files
# Predicted data
fileNameIn1 <- file.path(dir_data, "data/allcomp.txt.gz")
# download.file("https://insulatordb.uthsc.edu/download/allcomp.txt.gz", fileNameIn1)
# Experimental data
fileNameIn2 <- file.path(dir_data, "data/CTCFBSDB_all_exp_sites_Sept12_2012.txt.gz")
# download.file("https://insulatordb.uthsc.edu/download/CTCFBSDB_all_exp_sites_Sept12_2012.txt.gz", fileNameIn2)
# Output files
fileNameOut1 <- file.path(dir_data, "results/hg19.CTCFBSDB.CTCF_predicted_human.RData")
fileNameOut1.1 <- file.path(dir_data, "results/hg19.CTCFBSDB.CTCF_predicted_human.bed")
fileNameOut2 <- file.path(dir_data, "results/mm9.CTCFBSDB.CTCF_predicted_mouse.RData")
fileNameOut2.1 <- file.path(dir_data, "results/mm9.CTCFBSDB.CTCF_predicted_mouse.bed")
# fileNameOut3 <- file.path(dir_data, "results/hg19.CTCFBSDB.CTCF_experimental_human.RData")
# fileNameOut3.1 <- file.path(dir_data, "results/hg19.CTCFBSDB.CTCF_experimental_human.bed")
# fileNameOut4 <- file.path(dir_data, "results/mm9.CTCFBSDB.CTCF_experimental_mouse.RData")
# fileNameOut4.1 <- file.path(dir_data, "results/mm9.CTCFBSDB.CTCF_experimental_mouse.bed")
```

@@

hg19.CTCFBSDB.CTCF_predicted_human <- mtx_to_gr(mtx = mtx_human, genome_id = "hg38")
length(hg19.CTCFBSDB.CTCF_predicted_human)
summary(width(hg19.CTCFBSDB.CTCF_predicted_human))
mm9.CTCFBSDB.CTCF_predicted_mouse <- mtx_to_gr(mtx = mtx_mouse, genome_id = "mm10")
length(mm9.CTCFBSDB.CTCF_predicted_mouse)
summary(width(mm9.CTCFBSDB.CTCF_predicted_mouse))

# Save as RData object. subdir is the character name of the CTCF GRanges variable
save(list = hg19.CTCFBSDB.CTCF_predicted_human, file = fileNameOut1)
save(list = mm9.CTCFBSDB.CTCF_predicted_mouse, file = fileNameOut2)
# load(file = paste0(subdir, ".RData"))
# Save BED files
export.bed(hg19.CTCFBSDB.CTCF_predicted_human, fileNameOut1.1)
export.bed(mm9.CTCFBSDB.CTCF_predicted_mouse, fileNameOut2.1)
```

>>>>

# Input files
# Predicted data
fileNameIn1 <- file.path(dir_data, "data/allcomp.txt.gz")
# download.file("https://insulatordb.uthsc.edu/download/allcomp.txt.gz", fileNameIn1)
# Experimental data
fileNameIn2 <- file.path(dir_data, "data/CTCFBSDB_all_exp_sites_Sept12_2012.txt.gz")
# download.file("https://insulatordb.uthsc.edu/download/CTCFBSDB_all_exp_sites_Sept12_2012.txt.gz", fileNameIn2)
# Output files
fileNameOut1 <- file.path(dir_data, "results/hg18.CTCFBSDB.CTCF_predicted_human.RData")
fileNameOut1.1 <- file.path(dir_data, "results/hg18.CTCFBSDB.CTCF_predicted_human.bed")
fileNameOut2 <- file.path(dir_data, "results/mm8.CTCFBSDB.CTCF_predicted_mouse.RData")
fileNameOut2.1 <- file.path(dir_data, "results/mm8.CTCFBSDB.CTCF_predicted_mouse.bed")
# fileNameOut3 <- file.path(dir_data, "results/hg19.CTCFBSDB.CTCF_experimental_human.RData")
# fileNameOut3.1 <- file.path(dir_data, "results/hg19.CTCFBSDB.CTCF_experimental_human.bed")
# fileNameOut4 <- file.path(dir_data, "results/mm9.CTCFBSDB.CTCF_experimental_mouse.RData")
# fileNameOut4.1 <- file.path(dir_data, "results/mm9.CTCFBSDB.CTCF_experimental_mouse.bed")
```

@@

hg18.CTCFBSDB.CTCF_predicted_human <- mtx_to_gr(mtx = mtx_human, genome_id = "hg18")
length(hg18.CTCFBSDB.CTCF_predicted_human)
summary(width(hg18.CTCFBSDB.CTCF_predicted_human))
mm8.CTCFBSDB.CTCF_predicted_mouse <- mtx_to_gr(mtx = mtx_mouse, genome_id = "mm8")
length(mm8.CTCFBSDB.CTCF_predicted_mouse)
summary(width(mm8.CTCFBSDB.CTCF_predicted_mouse))

# Save as RData object. subdir is the character name of the CTCF GRanges variable
save(list = hg18.CTCFBSDB.CTCF_predicted_human, file = fileNameOut1)
save(list = mm8.CTCFBSDB.CTCF_predicted_mouse, file = fileNameOut2)
# load(file = paste0(subdir, ".RData"))
# Save BED files
export.bed(hg18.CTCFBSDB.CTCF_predicted_human, fileNameOut1.1)
export.bed(mm8.CTCFBSDB.CTCF_predicted_mouse, fileNameOut2.1)
```
